\textbf{\huge GRASS GIS}\\% \textsl{Efficiency through Freedom \& Transparency}

### 2015-07-21 grassflyer/flyer1/en/grassflyer.tex
grass-promo flyer: update grass flyer
git-svn-id: https://svn.osgeo.org/grass/grass-promo@65735 15284696-431f-4ddb-bdfa-cd5b030d7da7

GRASS (Geographic Resources Analysis Support System) is Free and Open Source Software for performing spatial analysis. It consists of more than 350 modules for processing vector (2D/3D), raster and voxel data. Many interfaces to other programs in related domains like geostatistics, databases, mapserver and even other GIS software exist. It is the largest Open Source GIS. It can serve as a Desktop GIS and as the backbone of a complete GIS infrastructure.

@@

GRASS is used in scientific applications, commercial settings and by public authorities all over the world. GRASS has shown strong potential for solving geospatial problems in numerous situations world-wide.

@@

GRASS was originally developed in the early 1980's by the US Army Construction Engineering Research Laboratories (USA-CERL) and was published as public domain software. When the USA-CERL withdrew from GRASS development, an international developer team assumed responsibility for the task. Since 1999, GRASS has been published as free software under the terms of the GNU General Public Licence.
\begin{myfig}[1.5ex]
\includegraphics[width=0.7\textwidth]{visibility}
\captionof{figure}{Viewshed analysis performed with GRASS}
\end{myfig}

\section{Open Source Philosophy}

The Open Source philosophy lets the user see the source code and structure of the program, which offers great transparency. Users can extend the program for their own needs. Immediate source code peer review increases the quality. With the help of the extension manager, new modules can be created without GRASS package source code.

@@

\begin{itemize}
\item Modular
\item Consists of more than 350 modules
\end{itemize}

@@

\begin{itemize}
\item ANSI C
\item GRASS-SWIG interface
\item Python for WebGIS applications
\item Java Version: JGRASS
\end{itemize}

@@

\begin{itemize}
\item Raster / Vector / Voxel data processing
\item 2D / 3D Raster / Vector modeling
\item Image manipulation
\item Vector topology / Network analysis
\item Geostatistics (Interface to R)
\end{itemize}

@@

\subsection{Raster file formats}
ASCII, ARC/GRID, E00, GIF, GMT, TIF, PNG, Vis5D, SURFER (.grd),\dots
\begin{myfig}
\includegraphics[width=0.7\textwidth]{isodist}
\captionof{figure}{Default GUI configuration showing GRASS network analysis capabilites}
\end{myfig}

@@

CEOS (SAR, SRTM, LANDSAT7 etc.), ERDAS LAN / IMG, HDF, LANDSAT TM/MSS, NHAP aerial photos, SAR, SPOT, \dots
\begin{myfig}[1.5ex]
\includegraphics[width=0.7\textwidth]{ndvi}
\captionof{figure}{Image processing options in GRASS}
\end{myfig}

@@

\begin{itemize}
\item PostgreSQL / PostGIS
\item MySQL
\item SQLite
\item ODBC
\item DBF
\end{itemize}

@@

\begin{itemize}
\item Mapping modules
\item NVIZ for visualization of 2.5D and 3D data (creation of animations \& flybys)
%\item{GMT export}
%item{VRML}
\item VTK, POVray
\item WebGIS via Mapserver, Python, etc.
\end{itemize}

@@

\begin{itemize}
\item Quantum GIS (Free geodata viewer and more)
\item R-Language (Statistics)
\item Gstat (Geostatistics)
\item UMN Mapserver (Webmapping)
\end{itemize}

@@

\begin{itemize}
%\begin{flushleft}
\item{Project Website: \\\GRASSurl}
\item{GRASS Wiki: \\\url{http://grass.osgeo.org/wiki}}
\item{GRASS Promotion Team: \\\url{malte@perlomat.de}}
\item{GRASS mailing lists: \\\url{http://grass.osgeo.org/community/support.php}}
%\end{flushleft}
\end{itemize}

@@

GRASS is a founding project of the Open Source Geospatial Foundation which has the aim to create high quality open source geospatial software. For further information visit the OSGeo homepage:
\begin{center}
\includegraphics[width=0.8\textwidth]{OSGeo_CMYK}\\
\url{http://www.osgeo.org}
\end{center}

>>>>

GRASS GIS (Geographic Resources Analysis Support System) is Free and Open Source Software for performing spatial analysis. It consists of \textbf{more than 400 modules for processing vector (2D/3D), raster, voxel and temporal data (4D)}. Many interfaces to other programs in related domains like geostatistics, databases, map web services and even other GIS software exist. It is the oldest and largest Free and Open Source GIS. It can serve as a Desktop GIS and as the backbone of a complete GIS infrastructure.

@@

GRASS GIS is used in scientific applications, commercial settings and by public authorities all over the world. GRASS GIS has shown strong potential for solving geospatial problems in numerous situations world-wide.

@@

GRASS GIS was originally developed in the early 1980's by the US Army Construction Engineering Research Laboratories (USA-CERL) and was published as public domain software. When the USA-CERL withdrew from GRASS GIS development, an international developer team assumed responsibility for the task. Since 1999, GRASS GIS has been published as free software under the terms of the GNU General Public Licence. Several people during years contributed to improve the software, they helped to add new functionality, speedup existing modules, make \textbf{GRASS GIS easier, more useful and powerful to everybody}. \newline

\begin{myfig}
\includegraphics[width=0.8\textwidth]{isodist}
\captionof{figure}{Default GUI configuration showing GRASS network analysis capabilites}
\end{myfig}

\section{Free and Open Source Philosophy}

The Free and Open Source philosophy lets the user see the source code and structure of the program, which offers great transparency. Users can extend the program for their own needs. Immediate source code peer review increases the quality. With the help of the extension manager, new modules can be created without GRASS GIS package source code.

@@

\begin{itemize}
\item Modular commands
\item Consists of more than 400 modules
\end{itemize}

@@

\begin{itemize}
\item ANSI C
\item GRASS-SWIG interface
\item Python API, scripting library and GUI
\end{itemize}

@@

\begin{itemize}
\item Raster / Vector / Voxel data processing
\item 2D / 3D Raster / Vector modeling
\item Image manipulation
\item Vector topology / Network analysis
\item Geostatistics (Interface to R)
\item Temporal dataset
\item WPS interface
\end{itemize}

@@

\subsection{Raster file formats}
ASCII, ARC/GRID, E00, GIF, GMT, TIF, PNG, Vis5D, SURFER (.grd),\dots
\begin{myfig}[1.ex]
\includegraphics[width=0.7\textwidth]{visibility}
\captionof{figure}{Viewshed analysis performed with GRASS}
\end{myfig}

@@

CEOS (SAR, SRTM, LANDSAT7 etc.), ERDAS LAN / IMG, HDF, LANDSAT TM/MSS, NHAP aerial photos, SAR, SPOT, MODIS \dots
% \begin{myfig}[1.5ex]
% \includegraphics[width=0.7\textwidth]{ndvi}
% \captionof{figure}{Image processing options in GRASS}
% \end{myfig}
\begin{myfig}
\includegraphics[width=0.7\textwidth]{mapswipe}
\captionof{figure}{MapSwipe tool showing differences before and after Japan Tsunami 2011}
\end{myfig}

@@

\begin{itemize}
\item SQLite
\item PostgreSQL / PostGIS
\item MySQL
\item ODBC
\item DBF
\end{itemize}

@@

\begin{itemize}
\item Mapping modules (animation, cartographic \dots)
\item NVIZ for visualization of 2.5D and 3D data (creation of animations \& flybys)
%\item{GMT export}
%item{VRML}
\item VTK, POVray
\item Web Services
\end{itemize}

@@

\begin{itemize}
\item QGIS (Free geodata viewer and more)
\item R-Language (Statistics)
\item Gstat (Geostatistics)
\item UMN MapServer (Webmapping)
\end{itemize}

@@

\begin{itemize}
% \begin{flushleft}
\item{Project Website: \\\GRASSurl}
\item{GRASS Wiki: \\\url{http://grass.osgeo.org/wiki}}
% \item{GRASS Promotion Team: \\\url{malte@perlomat.de}}
\item{GRASS mailing lists: \\\url{http://grass.osgeo.org/community}}
% \end{flushleft}
\end{itemize}

@@

GRASS is a founding project of the Open Source Geospatial Foundation which has the aim to create high quality open source geospatial software. For further information visit the OSGeo homepage:
\begin{center}
\includegraphics[width=0.7\textwidth]{OSGeo_CMYK}\\
\url{http://www.osgeo.org}
\end{center}
